A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
add missing newline
setup, only once per machine closes #6
mention our reproduction statement close #28 related #12
some changes in the example git_add(). I think there was an error in l.220. It should be git_commit() instea of git_add(), right?

If these commands detect that something is not installed or set up properly, they will alert you and give you detailed instructions (tailored to your operating system) to set up your computer.
Please make sure that all these commands pass before you continue with the tutorial.

@@

Could we use openpsychometrics.org data?
```

And you could commit it in Git.
For convenience, we use the [`gert`-package](https://github.com/r-lib/gert) [@R-gert] to interface with Git, but it does not make a difference:
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane?-->

```r
gert::git_add("idea.md")
gert::git_add("add a first concept")
```

@@

Could we use openpsychometrics.org data?
```

@@

A reproducible project should not only be theoretically reproducible, but it should be simple to reproduce.
Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
E.g. you can download any git repository with these commands:

>>>>

If these commands detect that something is not installed or set up properly, they will alert you and give you detailed instructions (tailored to your operating system) to set up your computer.
Please make sure that all these commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated per project.

@@

Can we use openpsychometrics.org data?
```

And you could commit it in Git.
For convenience, we use the [`gert`-package](https://github.com/r-lib/gert) [@R-gert], which wraps most git commands into R functions. Alternatively, we suggest to either work directly in the terminal (for example, RStudio offers a command shell with various options accessible in the Menu Tools -> Terminal), or work using the Git pane in RStudio that offers buttons for basic operations.
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane?-->

To commit your first changes to the project, start with staging all files to be included in the commit using `git_add()`. Here, we stage our idea collection in the file `idea.md` and then commit it to our local repository with a meaningful commit message that will later help us keep track of all the changes over time.

```r
gert::git_add("idea.md")
gert::git_commit("add a first concept")
```

@@

Can we use openpsychometrics.org data?
```

@@

A reproducible project should not only be theoretically reproducible, but it should be simple to reproduce.
Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
Figure \@ref(fig:readme) shows `r link("https://github.com/aaronpeikert/repro-tutorial#how-to-reproduce-this-manuscript", "the reproduction statement of this project")`.
E.g. you can download any git repository with these commands:
